An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-10-25 neurips-19/poly-embed.tex
inline comments

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessie Finocchiaro \\
 \texttt{jefi8453@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo Waggoner\\
 \texttt{bwag@colorado.edu}\\
 Microsoft Research, New York City
}

@@

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.
\jessie{R2 asked for more intuition on this definition... not sure what more to add}

\proposedadd{We focus on polyhedral losses in this context because, as Ramaswamy et al.~\cite[Section 1.2]{ramaswamy2018consistent} point out, smooth surrogates that estimate the conditional probability generally do much more than necessary, or practical in many cases.  In minimizing a polyhedral loss, they make the argument that one only learns what is necessary, in accordance with Vapnik's dictum~\cite[Section 1.9]{vapnik1999nature}.}

@@

\proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.  They are generally derived mathematically, rather than computationally.  These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}

>>>>

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessie Finocchiaro \\
 \texttt{jefi8453@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo Waggoner\\
 \texttt{bwag@colorado.edu}\\
 CU Boulder
}

@@

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.
\raft{CHANGED}
To motivate our focus on polyhedral losses, we echo Ramaswamy et al.~\cite[Section 1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the only candidates to achieve a low dimension $d$ above.

@@

\raf{Will shorten.}
\proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.  They are generally derived mathematically, rather than computationally.  These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}
